PMC Survey Data Analysis

### 2021-08-05 analysis.Rmd
citation analysis

library("wordcloud")
library("RColorBrewer")
library("wordcloud2")

@@

```
journalabbrev <- medline[grep("Title(s):",medline)]

jdf <- data.frame(journaltitle,journalabbrev)

m <- merge(jmetrics,jdf,by.x="Title",by.y="journaltitle")
dim(m)
mm <- m[,c("journalabbrev","SJR")]
dim(mm)

dim(x)
xm <- merge(x,mm,by.x="Journal",by.y="journalabbrev")
dim(xm)
tail(xm)

dim(x)
length(which(x$Journal %in% mm$journalabbrev))

x[which(! x$Journal %in% mm$journalabbrev),"Journal"]

mm$journalabbrev
head(x$Journal)

>>>>

library("wordcloud")
library("RColorBrewer")
library("wordcloud2")
library("reutils")
library("XML")
library("kableExtra")

@@

xm <- merge(x,mjdf,by.x="Journal",by.y="journalabbrev",all.x = TRUE)
dim(xm)
tail(xm)

## Article citations

```{r,cites}

get_pub_date <- function(PMCID) {
  res2 <- esummary(uid=PMCID, db = "pmc")
  res3 <- content(x=res2,as="text")
  res5 <- xmlToList(res3)
  d <- res5$DocumentSummarySet$DocumentSummary$EPubDate
  d <- gsub(" Jan ","-1-",d)
  d <- gsub(" Feb ","-2-",d)
  d <- gsub(" Mar ","-3-",d)
  d <- gsub(" Apr ","-4-",d)
  d <- gsub(" May ","-5-",d)
  d <- gsub(" Jun ","-6-",d)
  d <- gsub(" Jul ","-7-",d)
  d <- gsub(" Aug ","-8-",d)
  d <- gsub(" Sep ","-9-",d)
  d <- gsub(" Oct ","-10-",d)
  d <- gsub(" Nov ","-11-",d)
  d <- gsub(" Dec ","-12-",d)
  return(as.Date(d))
}

get_cites <- function(PMCID) {
  mylink <- elink(uid=PMCID , dbFrom="pmc", dbTo = "pubmed")
  PMID <- mylink[1]
  CITES <- elink(uid = PMID , dbFrom = "pubmed"  , linkname = "pubmed_pubmed_citedin" )
  N_CITES <- length(CITES[1])
  PUBDATE <- get_pub_date(PMCID)
  return(c(PMCID,PMID,N_CITES,PUBDATE))
}

PMCIDS <- as.numeric(gsub("PMC","",x$Pubmed.Central.ID))

# getcites needs to be fixed so that it can handle all the results
PMCIDS <- head(PMCIDS,100)
res <- lapply(X = PMCIDS, FUN = get_cites)
mx <- do.call(rbind,res)
mx <- apply(X = mx, MARGIN = 2, FUN = as.numeric)
df <- as.data.frame(mx)
colnames(df) <- c("PMCID","PMID","NumCites","Pubdate")

df %>% kbl %>% kable_paper("hover", full_width = F)

plot(df$Pubdate,df$NumCites)
mylm <- lm(df$NumCites ~ df$Pubdate)

mylm
